Simulation study in rectangular domain

### 2024-04-16 R/simulation_study/simulation_study_rect.Rmd
parallelization in simulation_study_rect + other stuff

# Import libraries and data

```{r}
#seed for reproducibility 
set.seed(1)

@@

# global variables

```{r}
#number of tracks
N_BATCH=1
N_ID=3

@@

We create a square with sides of length 8km.
```{r}

@@

```{r}

@@

```{r}

@@

```{r}
#observation times
Tmax=1*24 #max time in hour

hf=1/60 #1 minute time step

#high frequency time steps
times_hf=seq(0,Tmax,by=hf)
n_hf=length(times_hf)-1

@@

```{r}
#no measurement error (we cannot put 0 because only the log of this quantity is used)
sigma_obs_0=0.005
H0_hf=array(rep(sigma_obs_0^2*diag(2),n_hf*N_ID),dim=c(2,2,n_hf*N_ID))
#GPS measurement error 
sigma_obs_1=0.03
H1_hf=array(rep(sigma_obs_1^2*diag(2),n_hf*N_ID),dim=c(2,2,n_hf*N_ID))

@@

```{r}

@@

#constant nu
fnu_constant=function(cov_data,nu=1,sigma_re=0.3) {
    b=rnorm(1,mean=0,sd=sigma_re)
  return (nu+b)
}

@@

```{r}

@@

```{r}
SP_DF=5
#number of points
n <- 500

@@

```{r}
ExpShore=1/DistanceShore

@@

```{r}
sp_coeff_Dshore=m1$coefficients
sp_coeff_ExpShore=m2$coefficients
```

## Simulation with measurement errors and high frequency

@@

```{r, cache=TRUE,results='hide'}

#initialize data frame
data_rect_hf_ne=list()

  data=data.frame("y1"=NA,"y2"=NA,"time"=NA,"p1"=NA,"p2"=NA,"ID"=NA)

  for (i in 1:N_ID) {

@@

    data_sim=res$sim
    data_sim$ID=factor(rep(i,length(data_sim$y1)))
    data_shore=res$shore[,c("p1","p2")]
    data=rbind(data,cbind(data_sim,data_shore))
  }

  #for the first value we cannot compute the angle theta
  data=data[-1,]
  data_rect_hf_ne[[paste("BATCH",k,sep="")]]=data
}

@@

```{r}
count=0
for (k in 1:length(names(data_rect_hf_ne))) {

  data=data_rect_hf_ne[[paste("BATCH",k,sep="")]]
  for (id in unique(data$ID)) {
    sub_data=data[data$ID==id,]
    if (nrow(sub_data) < n_hf) {
      count=count+1
      cat("BATCH",k,id,"\n",sep="")
    }
  }
}
cat(count/(N_BATCH*N_ID)*100,"percent of the samples reached land")
```

@@

```{r}

@@

```{r, cache=TRUE,results='hide'}

#initialize data frame
data_rect_hf_e=list()

  data=data.frame("y1"=NA,"y2"=NA,"time"=NA,"p1"=NA,"p2"=NA,"ID"=NA)

  for (i in 1:N_ID) {

@@

    data_sim=res$sim
    data_sim$ID=factor(rep(i,length(data_sim$y1)))
    data_shore=res$shore[,c("p1","p2")]
    data=rbind(data,cbind(data_sim,data_shore))
  }

  #for the first value we cannot compute the angle theta
  data=data[-1,]
  data_rect_hf_e[[paste("BATCH",k,sep="")]]=data
}
```

@@

```{r}
count=0
for (k in 1:length(names(data_rect_hf_e))) {

@@

```{r}

@@

```{r}

@@

```{r,cache=TRUE}

#estimation with tensor splines
formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,ExpShore,k=SP_DF,bs="cs"))
par0 <- c(0,0,1,4,0)

crcvm_rect_hf_ne1 <- SDE$new(formulas = formulas,data = data_rect_hf_ne$BATCH1,type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H0_hf))
crcvm_rect_hf_ne1$fit(method="BFGS")
```

#### Plot estimated smooth parameter omega in 3D

```{r}
xmin=list("theta"=-pi,"ExpShore"=1/2)
xmax=list("theta"=pi,"ExpShore"=1/0.3)
xlabel=list("ExpShore"="Distance to shore")
link=list("ExpShore"=(\(x) 1/x))
true_smooths=list("omega"=fomega)
res=crcvm_rect_hf_ne1$get_all_plots(baseline=NULL,model_name="crcvm_rect_hf_ne1",xmin=xmin,xmax=xmax,
                                    xlabel=xlabel,link=link,show_CI="pointwise",true_smooths=true_smooths,save=TRUE)
res$fe_omega_theta_ExpShore
```

```{r}

p=crcvm_rect_hf_ne1$plot_violin_coeff(model_name="crcvm_rect_hf_ne1",substring="omega",true_coeff=true_coeff,save=TRUE)

@@

```{r,cache=TRUE}

@@

  #distance to shore
  Dshore=sqrt(normal[1]^2+normal[2]^2)
  if (Dshore>0.5){
    return (0)
  }
  else if (Dshore<0.01) {
    return (100)
  }
  else {
    return (1/Dshore)
  }
}

@@

atw=list("ExpShore"=fExpShore,"AngleNormal"=fangle)
sim_data=crcvm_rect_hf_ne1$simulate(z0=x0[1,],data=crcvm_rect_hf_ne1$data(),atw=atw,land=domain)

@@

```{r}

@@

###  UseDistanceShore covariate and tensor splines ti

@@

```{r,cache=TRUE}
#estimation with tensor splines
formulas <- list(mu1=~1,mu2=~1,tau=~1,
                 nu=~1,omega=~te(theta,DistanceShore,k=SP_DF,bs="cs"))
par0 <- c(0,0,1,4,0)

crcvm_rect_hf_ne2 <- SDE$new(formulas = formulas,data = data_rect_hf_ne[data_rect_hf_ne$ID==1,],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2","nu","tau"),
                      other_data=list("H"=H0_hf))
crcvm_rect_hf_ne2$fit(method="BFGS")
```

@@

```{r}
xmin=list("theta"=-pi,"DistanceShore"=0.3)
xmax=list("theta"=pi,"DistanceShore"=2)
res=crcvm_rect_hf_ne2$get_all_plots(baseline=NULL,model_name="crcvm_rect_hf_ne2",xmin=xmin,xmax=xmax,
                                    xlabel=xlabel,link=link,show_CI="pointwise",true_smooths=true_smooths,save=TRUE)
res$fe_omega_theta_DistanceShore
```

@@

```{r}

p=crcvm_rect_hf_ne2$plot_violin_coeff(model_name="crcvm_rect_hf_ne2",substring="omega",true_coeff=true_coeff,save=TRUE)

@@

## Estimate from high frequency data with error :

@@

```{r, cache=TRUE}
#estimation with tensor splines
formulas <- list(mu1=~1,mu2=~1,tau=~1,
                 nu=~1,omega=~te(theta,ExpShore,k=5,bs="cs"))
par0 <- c(0,0,1,4,0)

crcvm_rect_hf_e1 <- SDE$new(formulas = formulas,data = data_rect_hf_e[data_rect_hf_e$ID==1,],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2","nu","tau"),
                      other_data=list("H"=H1_hf))
crcvm_rect_hf_e1$fit(method="BFGS")
```

#### Plot estimated smooth in 3D

```{r}
xmin=list("theta"=-pi,"ExpShore"=1/2)
xmax=list("theta"=pi,"ExpShore"=1/0.3)
xlabel=list("ExpShore"="Distance to shore")
link=list("ExpShore"=(\(x) 1/x))
true_smooths=list("omega"=fomega)
res=crcvm_rect_hf_e1$get_all_plots(baseline=NULL,model_name="crcvm_rect_hf_e1",xmin=xmin,xmax=xmax,
                                    xlabel=xlabel,link=link,show_CI="pointwise",true_smooths=true_smooths,save=TRUE)
res$fe_omega_theta_ExpShore
```

```{r}

@@

p=crcvm_rect_hf_e1$plot_violin_coeff(model_name="crcvm_rect_hf_e1",substring="omega",true_coeff=true_coeff,save=TRUE)

@@

@@

```{r,cache=TRUE}
#estimation with tensor splines
formulas <- list(mu1=~1,mu2=~1,tau=~1,
                 nu=~1,omega=~te(theta,DistanceShore,k=SP_DF,bs="cs"))
par0 <- c(0,0,1,4,0)

crcvm_rect_hf_e2 <- SDE$new(formulas = formulas,data = data_rect_hf_e[data_rect_hf_e$ID==1,],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2","nu","tau"),
                      other_data=list("H"=H1_hf))
crcvm_rect_hf_e2$fit(method="BFGS")
```

#### Plot estimated smooth in 3D

```{r}
xmin=list("theta"=-pi,"DistanceShore"=0.3)
xmax=list("theta"=pi,"DistanceShore"=2)
res=crcvm_rect_hf_e2$get_all_plots(baseline=NULL,model_name="crcvm_rect_hf_e2",xmin=xmin,xmax=xmax,
                                    xlabel=xlabel,link=link,show_CI="pointwise",true_smooths=true_smooths,save=TRUE)
res$fe_omega_theta_DistanceShore
```

```{r}

@@

p=crcvm_rect_hf_e2$plot_violin_coeff(model_name="crcvm_rect_hf_e2",substring="omega",true_coeff=true_coeff,save=TRUE)

@@

>>>>

# SET UP

## Import libraries

```{r libraries}
#seed for reproducibility 
set.seed(1)

#parallel computing
library(foreach)
library(doParallel)

@@

## global variables

```{r global variables}
#number of batch
N_BATCH=10

#number of individual tracks per batch
N_ID=3

#duration of each track in hour
TMAX=1*24

@@

We create a square with sides of length 8km.

```{r create rectangle}

@@

```{r plot rectangle}

@@

```{r initial positions}

@@

```{r time steps}
#time step
hf=1/60

#high frequency time points
times_hf=seq(0,TMAX,by=hf)
n_hf=length(times_hf)-1

@@

```{r measurement error}
#no measurement error (we cannot put 0 because only the log of this quantity is used)
sigma_obs_0=0.005
H0_hf=array(rep(sigma_obs_0^2*diag(2),n_hf*N_ID),dim=c(2,2,n_hf*N_ID))
#GPS measurement error 
sigma_obs_1=0.03
H1_hf=array(rep(sigma_obs_1^2*diag(2),n_hf*N_ID),dim=c(2,2,n_hf*N_ID))

@@

```{r smooth parameters}

@@

#constant nu
fnu_constant=function(cov_data,nu=4,sigma_re=0.3) {
    b=rnorm(1,mean=0,sd=sigma_re)
  return (nu+b)
}

@@

```{r plot smooth parameters}

@@

```{r approximate smooth omega with DistanceShore splines}

#number of points
n <- 1000

@@

```{r approximate smooth omega with ExpShore splines}
ExpShore=1/DistanceShore

@@

```{r estimated spline coeffs}
sp_coeff_Dshore=m1$coefficients
sp_coeff_ExpShore=m2$coefficients
```

### Define spline smooth functions for omega based on the approximations

```{r spline smooth omega definition}

fomega_splines=function(cov_data) {

  if (is.null(cov_data$ExpShore)){
    omega=predict(m1,newdata=cov_data)
  }
  else if (is.null(cov_data$DistanceShore)){
    omega=predict(m2,newdata=cov_data)
  }

  return(as.numeric(omega))
}

### Plot

```{r plot spline smooth omega}

Dshore=seq(from=0.3,to=2,length.out=30)
theta=seq(from=-pi,to=pi,length.out=30)
grid<- as.data.frame(expand.grid(DistanceShore,theta))
colnames(grid)=c("DistanceShore","theta")
true_par=grid
true_par$omega=fomega_splines(grid)

plot_true_omega <- plot_ly(true_par,type = "mesh3d",
                         x = ~theta,y = ~DistanceShore,z=~omega,intensity=~omega,
                         colors=colorRamp(c("blue", "lightblue", "chartreuse3", "yellow", "red")))%>%
                layout(title=paste("True omega"),scene=list(xaxis = list(title = "Theta",showgrid = F),
                                                                 yaxis = list(title = "Distance to shore",showgrid = F),
                                                            zaxis = list(title = "omega")))

plot_true_omega
```

## Simulation with low measurement errors and high frequency

@@

```{r parallel generate hf low errors samples}

#setup parallel backend to use many processors
cores=detectCores()
cl <- makeCluster(cores[1]-1) #not to overload your computer
registerDoParallel(cl)

data_rect_hf_ne <- foreach(i=1:N_BATCH,.packages=c("progress","MASS","sf","foreach")) %dopar% {
  data=foreach (i=1:N_ID,.combine='rbind') %do% {

@@

    data_sim=res$sim
    data_sim$ID=factor(rep(i,length(data_sim$y1)))
    data_shore=res$shore[,c("p1","p2")]
    cbind(data_sim,data_shore)
  }
  data 
}

#stop cluster
stopCluster(cl)

names(data_rect_hf_ne)=paste("BATCH",1:N_BATCH,sep="")
```

@@

```{r percentage of low error samples that reached land}
count=0
for (k in 1:length(names(data_rect_hf_ne))) {

  data=data_rect_hf_ne[[paste("BATCH",k,sep="")]]
  for (id in unique(data$ID)) {
    sub_data=data[data$ID==id,]
    if (nrow(sub_data) < n_hf) {
      count=count+1
      cat(paste("BATCH",k,sep=""),":",id,"\n",sep=" ")
    }
  }
}
cat(count/(N_BATCH*N_ID)*100,"percent of the samples reached land")
```

@@

```{r plot one batch low error samples}

@@

```{r high error samples, cache=TRUE,results='hide'}
#setup parallel backend to use many processors
cores=detectCores()
cl <- makeCluster(cores[1]-1) #not to overload your computer
registerDoParallel(cl)

data_rect_hf_e <- foreach(i=1:N_BATCH,.packages=c("progress","MASS","sf","foreach")) %dopar% {
  data=foreach (i=1:N_ID,.combine='rbind') %do% {

@@

    data_sim=res$sim
    data_sim$ID=factor(rep(i,length(data_sim$y1)))
    data_shore=res$shore[,c("p1","p2")]
    cbind(data_sim,data_shore)
  }
  data 
}

#stop cluster
stopCluster(cl)

#change names of the list elements
names(data_rect_hf_e)=paste("BATCH",1:N_BATCH,sep="")
```

@@

```{r percentage of high error samples that reached land}
count=0
for (k in 1:length(names(data_rect_hf_e))) {

@@

```{r plot one batch of high error samples}

@@

```{r compute covs}

@@

```{r estimate te ExpShore for low error samples,cache=TRUE}

#setup parallel backend to use many processors
cores=detectCores()
cl <- makeCluster(cores[1]-1) #not to overload your computer
registerDoParallel(cl)

crcvm_rect_hf_ne1<- foreach(i=1:N_BATCH,.packages=c("smoothSDE")) %dopar% {
  #estimation with tensor splines
  formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,ExpShore,k=SP_DF,bs="cs"))
  par0 <- c(0,0,1,1,0)
  m <- SDE$new(formulas = formulas,data = data_rect_hf_ne[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H0_hf))
  m$fit(method="BFGS")
  m 
}

#stop cluster
stopCluster(cl)

names(crcvm_rect_hf_ne1)=paste("BATCH",1:N_BATCH,sep="")

#### Plot estimated smooth parameter omega in 3D for one batch

```{r plot estimates te ExpShore for one batch of low error samples}
xmin=list("theta"=-pi,"ExpShore"=1/2)
xmax=list("theta"=pi,"ExpShore"=1/0.3)
xlabel=list("ExpShore"="Distance to shore")
link=list("ExpShore"=(\(x) 1/x))
true_smooths=list("omega"=fomega_splines)
res=crcvm_rect_hf_ne1$BATCH1$get_all_plots(baseline=NULL,model_name="crcvm_rect_hf_ne1",xmin=xmin,xmax=xmax,
                                    xlabel=xlabel,link=link,show_CI="pointwise",true_smooths=true_smooths,save=TRUE)
res$fe_omega_theta_ExpShore
```

#### Violin plot of the estimated spline coefficients for one batch

```{r violin plots spline coeff te ExpShore for one batch of low error samples}

true_coeff=data.frame(value=sp_coeff_ExpShore,name=c(paste("omega.",names(sp_coeff_ExpShore),sep="")))
rownames(true_coeff)=NULL

p=crcvm_rect_hf_ne1$BATCH1$plot_violin_coeff(model_name="crcvm_rect_hf_ne1",substring="omega",true_coeff=true_coeff,save=TRUE)

#### Violin plot of the estimated spline coefficients for all batches

```{r violin plots spline coeff te ExpShore all batches with low measurement error}

n_coeffs=length(sp_coeff_ExpShore)
coeffs_df=data.frame("estimate"=NA,"coeff_name"=NA)

for (k in 1:N_BATCH) {
  m<-crcvm_rect_hf_ne1[[paste("BATCH",k,sep="")]]
  coeffs=m$coeff_re()
  coeff_names=rownames(coeffs)
  coeff_values=as.numeric(coeffs)
  sub_index=grepl("omega",coeff_names)
  sub_coeffs_df=data.frame("estimate"=coeff_values[sub_index],"coeff_name"=factor(coeff_names[sub_index]))
  coeffs_df=rbind(coeffs_df,sub_coeffs_df)
}

#remove initialization row
coeffs_df=coeffs_df[-1,]

p=ggplot()+geom_violin(data=coeffs_df,aes(x=coeff_name,y=estimate,fill=coeff_name))+
                xlab(" ")+labs(fill = "Estimated coefficients")+
                theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
                geom_point(data = true_coeff, aes(x = name, y = value), color = "red", size = 1,shape=4)

ggsave("all_batches_coeffs_crcvm_rect_hf_ne1.png",plot=p,path="crcvm_rect_hf_ne1")

@@

```{r simulate fitted te ExpShore low error samples,cache=TRUE}

@@

  #distance to shore
  Dshore=sqrt(normal[1]^2+normal[2]^2)
  if (Dshore<0.01) {
    return (100)
  }
  else {
    return (1/Dshore)
  }
}

@@

atw=list("ExpShore"=fExpShore,"AngleNormal"=fangle)
sim_data=crcvm_rect_hf_ne1$BATCH1$simulate(z0=x0[1,],data=crcvm_rect_hf_ne1$BATCH1$data(),atw=atw,land=domain)

@@

```{r plot sim te ExpSHore low error samples}

@@

###  Use DistanceShore covariate and tensor splines te

@@

```{r estimate te DistanceShore for low error samples,cache=TRUE}
#estimation with tensor splines
formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,DistanceShore,k=SP_DF,bs="cs"))

crcvm_rect_hf_ne2=list()
for (k in 1:N_BATCH) {
  m <- SDE$new(formulas = formulas,data = data_rect_hf_ne[[paste("BATCH"),k,sep=""]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H0_hf))
  m$fit(method="BFGS")
  crcvm_rect_hf_ne2[[paste("BATCH",k,sep="")]]<-m
}
```

@@

```{r plot estimates te DistanceShore for one batch of low error samples}
xmin=list("theta"=-pi,"DistanceShore"=0.3)
xmax=list("theta"=pi,"DistanceShore"=2)
res=crcvm_rect_hf_ne2$BATCH1$get_all_plots(baseline=NULL,model_name="crcvm_rect_hf_ne2",xmin=xmin,xmax=xmax,
                                    xlabel=xlabel,link=link,show_CI="pointwise",true_smooths=true_smooths,save=TRUE)
res$fe_omega_theta_DistanceShore
```

@@

```{r violin plots spline coeffs te DistanceShore for one batch of low error sample}

true_coeff=data.frame(value=sp_coeff_Dshore,name=c(paste("omega.",names(sp_coeff_Dshore),sep="")))
rownames(true_coeff)=NULL

p=crcvm_rect_hf_ne2$BATCH1$plot_violin_coeff(model_name="crcvm_rect_hf_ne2",substring="omega",
                                             true_coeff=true_coeff,save=TRUE)

@@

#### Violin plot of the estimated spline coefficients for all batches

```{r violin plots spline coeff te DistanceShore all batches with low measurement error}

n_coeffs=length(sp_coeff_DShore)
coeffs_df=data.frame("estimate"=NA,"coeff_name"=NA)

for (k in 1:N_BATCH) {
  m<-crcvm_rect_hf_ne2[[paste("BATCH",k,sep="")]]
  coeffs=m$coeff_re()
  coeff_names=rownames(coeffs)
  coeff_values=as.numeric(coeffs)
  sub_index=grepl("omega",coeff_names)
  sub_coeffs_df=data.frame("estimate"=coeff_values[sub_index],"coeff_name"=factor(coeff_names[sub_index]))
  coeffs_df=rbind(coeffs_df,sub_coeffs_df)
}

#remove initialization row
coeffs_df=coeffs_df[-1,]

p=ggplot()+geom_violin(data=coeffs_df,aes(x=coeff_name,y=estimate,fill=coeff_name))+
                xlab(" ")+labs(fill = "Estimated coefficients")+
                theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
                geom_point(data = true_coeff, aes(x = name, y = value), color = "red", size = 1,shape=4)

ggsave("all_batches_coeffs_crcvm_rect_hf_ne2.png",plot=p,width=10,height=5,path="crcvm_rect_hf_ne2")

## Estimate from high frequency data with error

@@

```{r estimate te ExpShore for high error samples, cache=TRUE}
#estimation with tensor splines
formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,ExpShore,k=SP_DF,bs="cs"))

crcvm_rect_hf_e1=list()
for (k in 1:N_BATCH) {
  m <- SDE$new(formulas = formulas,data = data_rect_hf_e[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H0_hf))
  m$fit(method="BFGS")
  crcvm_rect_hf_e1[[paste("BATCH",k,sep="")]]<-m
}
```

#### Plot estimated smooth in 3D for one batch

```{r plots estimates te ExpShore for one batch of high error samples}
xmin=list("theta"=-pi,"ExpShore"=1/2)
xmax=list("theta"=pi,"ExpShore"=1/0.3)
xlabel=list("ExpShore"="Distance to shore")
link=list("ExpShore"=(\(x) 1/x))
true_smooths=list("omega"=fomega)
res=crcvm_rect_hf_e1$BATCH1$get_all_plots(baseline=NULL,model_name="crcvm_rect_hf_e1",xmin=xmin,xmax=xmax,
                                    xlabel=xlabel,link=link,show_CI="pointwise",true_smooths=true_smooths,save=TRUE)
res$fe_omega_theta_ExpShore
```

#### Violin plot of the estimated spline coefficients for one batch

```{r violin plots spline coeffs te ExpShore for one batch of high error sample}

@@

p=crcvm_rect_hf_e1$BATCH1$plot_violin_coeff(model_name="crcvm_rect_hf_e1",substring="omega",true_coeff=true_coeff,save=TRUE)

@@

#### Violin plot of the estimated spline coefficients for all batches

```{r violin plots spline coeff te ExpShore all batches with high measurement error}

n_coeffs=length(sp_coeff_ExpShore)
coeffs_df=data.frame("estimate"=NA,"coeff_name"=NA)

for (k in 1:N_BATCH) {
  m<-crcvm_rect_hf_e1[[paste("BATCH",k,sep="")]]
  coeffs=m$coeff_re()
  coeff_names=rownames(coeffs)
  coeff_values=as.numeric(coeffs)
  sub_index=grepl("omega",coeff_names)
  sub_coeffs_df=data.frame("estimate"=coeff_values[sub_index],"coeff_name"=factor(coeff_names[sub_index]))
  coeffs_df=rbind(coeffs_df,sub_coeffs_df)
}

#remove initialization row
coeffs_df=coeffs_df[-1,]

p=ggplot()+geom_violin(data=coeffs_df,aes(x=coeff_name,y=estimate,fill=coeff_name))+
                xlab(" ")+labs(fill = "Estimated coefficients")+
                theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
                geom_point(data = true_coeff, aes(x = name, y = value), color = "red", size = 1,shape=4)

ggsave("all_batches_coeffs_crcvm_rect_hf_e1.png",plot=p,width=10,height=5,path="crcvm_rect_hf_e1")

ggplotly(p)

@@

```{r estimate te DistanceShore for high error samples,cache=TRUE}
#estimation with tensor splines
formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,DistanceShore,k=SP_DF,bs="cs"))

crcvm_rect_hf_e2=list()

for (k in 1:N_BATCH) {
  m <- SDE$new(formulas = formulas,data = data_rect_hf_e[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H0_hf))
  m$fit(method="BFGS")
  crcvm_rect_hf_e2[[paste("BATCH",k,sep="")]]<-m
}
```

#### Plot estimated smooth in 3D for one batch

```{r plots estimates te DistanceShore for one batch of high error samples}
xmin=list("theta"=-pi,"DistanceShore"=0.3)
xmax=list("theta"=pi,"DistanceShore"=2)
res=crcvm_rect_hf_e2$BATCH1$get_all_plots(baseline=NULL,model_name="crcvm_rect_hf_e2",xmin=xmin,xmax=xmax,
                                    xlabel=xlabel,link=link,show_CI="pointwise",true_smooths=true_smooths,save=TRUE)
res$fe_omega_theta_DistanceShore
```

#### Violin plot of the estimated spline coefficients for one batch

```{r violin plots spline coeffs te DistanceShore for one batch of high error sample}

@@

p=crcvm_rect_hf_e2$BATCH1$plot_violin_coeff(model_name="crcvm_rect_hf_e2",substring="omega",true_coeff=true_coeff,save=TRUE)

@@

#### Violin plot of the estimated spline coefficients for all batches

```{r violin plots spline coeff te DistanceShore all batches with high measurement error}

n_coeffs=length(sp_coeff_DShore)
coeffs_df=data.frame("estimate"=NA,"coeff_name"=NA)

for (k in 1:N_BATCH) {
  m<-crcvm_rect_hf_e2[[paste("BATCH",k,sep="")]]
  coeffs=m$coeff_re()
  coeff_names=rownames(coeffs)
  coeff_values=as.numeric(coeffs)
  sub_index=grepl("omega",coeff_names)
  sub_coeffs_df=data.frame("estimate"=coeff_values[sub_index],"coeff_name"=factor(coeff_names[sub_index]))
  coeffs_df=rbind(coeffs_df,sub_coeffs_df)
}

#remove initialization row
coeffs_df=coeffs_df[-1,]

p=ggplot()+geom_violin(data=coeffs_df,aes(x=coeff_name,y=estimate,fill=coeff_name))+
                xlab(" ")+labs(fill = "Estimated coefficients")+
                theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
                geom_point(data = true_coeff, aes(x = name, y = value), color = "red", size = 1,shape=4)

ggsave("all_batches_coeffs_crcvm_rect_hf_e2.png",plot=p,width=10,height=5,path="crcvm_rect_hf_e2")
```
